{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-28 brains-protocol.tex
Add notice on human/automatic reproduction

Note that since we only consider substitutions and not faithful copies, we measure the features of an alteration \emph{knowing that there has been an alteration}, and we do not take invariant quotations into account.  Indeed, in the first case we know there has been a human reformulation, whereas in the second case it is impossible to know whether there has been perfect human reformulation or simply digital copy-pasting of a source (``{\sc Ctrl-C}/{\sc Ctrl-V}'').

>>>>

Note that since we only consider substitutions and not faithful copies, we measure the features of an alteration \emph{knowing that there has been an alteration}, and we do not take invariant quotations into account.  Indeed, in the first case we know there has been a human reformulation, whereas in the second case it is impossible to know whether there has been perfect human reformulation or simply digital copy-pasting of a source (``{\sc Ctrl-C}/{\sc Ctrl-V}'').
\rk{Recognize that this can be a sub-sample of real human manual Ctrl-C/V, since we don't have access to successful manual copy by the brain. No need to suppose this sample is representative: we focus on when there is a transformation, and that's the process we study (since we have no access to the difference between manual and automatic). We also therefore suppose that manual copy and manual transformation are potentially different processes, and can be studied separately profitably.}
